---
title: "p8105_hw5_hc3212"
author: "Hening CUi"
date: "11/14/2021"
output: github_document
---

```{r,echo = FALSE, message = FALSE}
library (tidyverse)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 0.6,
  out.width = "90%"
)

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_color_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the homocide data.

```{r read_data}
homo_df =
  read.csv("homicide-data.csv", na = c("", "Unknown")) 
```

The Washington Post collected data of criminal homicides over the past decade in different cities. The data set has `r nrow(homo_df)` cases, and `r ncol(homo_df)` variables which included the time, location and type of the killing, whether an arrest was made and basic demographic information about each victim.

```{r clean_data}
homo_clean =
  homo_df %>% 
  mutate(city_state = str_c(city, ",", state),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa,AL") 

homo_clean %>% 
  select(-city, -state) %>% 
  group_by(city_state) %>% 
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n()) %>% 
  knitr::kable()
```

Done the prop test of Baltimore, MD.

```{r}
balti_df =
  homo_clean %>% 
  filter(city_state == "Baltimore,MD")

balti_summary =     
  balti_df %>% 
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n())

balti_test =
  prop.test(x = balti_summary %>% pull(unsolved), 
          n = balti_summary %>% pull(n))

balti_test %>% 
  broom::tidy()
```
Now get test for each city.

Write the function first.

```{r prop_function}
prop_test_function = function(city_df){
  city_summary =     
    city_df %>% 
    summarize(unsolved = sum(resolution == "unsolved"),
              n = n())

  city_test =
    prop.test(x = city_summary %>% pull(unsolved), 
              n = city_summary %>% pull(n))

  return(city_test)
}
```

Lets run thorough other cities.


```{r iterate_through_city, warning = FALSE}
result_df =
  homo_clean %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_res = map(data, prop_test_function),
    tidy_res = map(test_res, broom::tidy)
  ) %>% 
  select(city_state, tidy_res) %>% 
  unnest(tidy_res) %>% 
  select(city_state, estimate, starts_with("conf"))
```

```{r another_method}
also_res_df =
  homo_clean %>% 
  select(-city, -state) %>% 
  group_by(city_state) %>% 
  summarize(unsolved = sum(resolution == "unsolved"),
            n = n()) %>% 
  mutate(test_res = map2(unsolved, n, prop.test),
         tidy_res = map(test_res, broom::tidy)
  ) %>% 
  select(city_state, tidy_res) %>% 
  unnest(tidy_res) %>% 
  select(city_state, estimate, starts_with("conf"))
```

Now create the plots!

```{r bar_plot}
result_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
```






## Problem 2

Creat a function to read data.

```{r read_data_function}
read = function(name) {
  path = str_c("./data/", name)
  obser = read.csv(path)
  return(obser)
}
```

Reading the data and tidy it.

```{r tidy_data}
study_df = tibble(
  filename = list.files("data" )
) %>% 
  mutate(outputlist = purrr::map(.x = as.character(filename), ~read(.x))) %>% 
  unnest(outputlist) %>% 
  mutate(subject_ID = substr(filename, 1, 6 ),
           arm = substr(filename, 1, 3)) %>% 
  select(-filename) %>% 
  relocate(subject_ID, arm) %>% 
  janitor::clean_names() %>% 
  drop_na() %>% 
  pivot_longer(
    cols = week_1:week_8,
    names_to = "week",
    values_to = "value"
  ) %>% 
  mutate(week = substr(week, 6, 6))
  
```

Make the spaghetti plot.

```{r spaghetti, fig.width=9, message=FALSE, warning=FALSE}
study_df %>% 
  ggplot(aes(x = as.numeric(week), y = value, color = as.factor(subject_id))) +
  geom_line() + geom_point(aes(shape = as.factor(arm)), size = 2.5, alpha = 0.5) +
  labs(
    title = "The obervation of subject over time",
    y = "obervation value", 
    x = "Week",
    ) +
  scale_colour_hue("Subject_id")+
  scale_shape("Arm")
```
It could find from the graph that most experiment group have higher observation value than the control group.

## Problem 3

Load iris dataset.

```{r load_data}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Write the function of refill missing data

```{r missing_function}
missing = function(miss) {
  
  if(is.numeric(miss)){
    mean_miss = round(mean(miss, na.rm = TRUE), digits = 2)
    miss = replace_na(miss, mean_miss)
  }
  
  if (is.character(miss)){
    miss = replace_na(miss, "virginica")
  }
  
  return(miss)
}


```


Refill the data, and build new data set

```{r refill_data}
iris_correct = map(iris_with_missing, missing) %>% 
  bind_cols()

iris_correct
```


